Meaning of simple rules in investment strategies of algorithmic trading

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
that there exists

It is easy to see that the majority of these excellent traders succeed within a certain period of time, and today the implementation of their methods gives poor results. This contradicts the general philosophy of these practitioners (but not all of them), that exists mysterious patterns or rules, that are characteristic for specific markets, which provide success.

>>>>

It is easy to see that the majority of these excellent traders succeed within a certain period of time, and today the implementation of their methods gives poor results. This contradicts the general philosophy of these practitioners (but not all of them), that there exists mysterious patterns or rules, that are characteristic for specific markets, which provide success.
